|

### 2019-11-18 analysis/paper/paper.Rmd
Polish default vs. median LAI plot & cap

```{r default-median-flux, fig.cap = default_median_flux_cap}
### Figure 4
default_median_flux_cap <- paste(
  htmlfig(),
  "Comparing results of ED2 with default parameters and",
  "posterior median parameters from trait meta-analysis",
  "across different strucures."
)
fig("default-median-fluxes.png")
```

@@

```{r default-median-lai, fig.cap = default_median_lai_cap}
### Figure 5
default_median_lai_cap <- paste(
  htmlfig(),
  "Comparing results of ED2 PFT-level LAI",
  "with default parameters",
  "posterior median parameters from trait meta-analysis",
  "across different strucures."
)
fig("default-median-lai.png")
```

>>>>

```{r default-median-flux, fig.cap = default_median_flux_cap}
### Figure 4
default_median_flux_cap <- paste(
  htmlfig(),
  "ED-2.2 predictions of mean annual",
  "gross (GPP) and net primary productivity (NPP)",
  "and autotrophic respiration (RA) from simulations using",
  "ED-2.2 default parameter values (red) and",
  "posterior median parameters from trait meta-analysis (blue)",
  "across different strucures."
)
fig("default-median-fluxes.png")
```

@@

```{r default-median-lai, fig.cap = default_median_lai_cap}
### Figure 5
default_median_lai_cap <- paste(
  htmlfig(),
  "ED-2.2 predictions of mean growing season leaf area index (LAI)",
  "by plant functional type (PFT), using",
  "ED-2.2 default parameter values (top) and",
  "posterior median parameters from trait meta-analysis (bottom)",
  "across different strucures."
)
fig("default-median-lai.png")
```
